Yoghurt under stress

### 2014-09-18 plis_beamer.tex
Adapt to wall slip workshop. Fix broken tex. tikzpictures re-generated for each overlay.

\bigskip
\begin{tabu}{X[c]X[c]c}
\includegraphics[height=0.3\textheight,clip=true,trim=3cm 7cm  2cm 5cm]{Mathieu}&
\includegraphics[height=0.3\textheight]{Thomas}&
\includegraphics[height=0.3\textheight]{Seb}\\
Mathieu Nespoulous & Thomas Gibaud & Sebastien Manneville\\
Associate Professor & CNRS researcher & Professor\\
Aix-Marseille Université & E.N.S. Lyon & E.N.S. Lyon\\
\end{tabu}

@@

%\tikzset{external/force remake}
\begin{frame}{Over-acidification: Faster but weaker}
\begin{tikzpicture}
\begin{axis}[
	height=0.8\textheight,
	width=\textwidth,
	xlabel={time (h)}, ylabel={$G^\prime$ (\si{\pascal})},
	cycle list name=earthy,
	no marks,
	xmin=0, xmax=20,ymin=0,
	]
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1_Y265.prise} node[anchor=base west] {1\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1.25_Y277.prise} node[anchor=base west] {1.25\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1.5_Y275.prise} node[anchor=base west] {1.5\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL2_Y268.prise} node[anchor=base west] {2\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL3_Y270.prise} node[anchor=base west] {3\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL4_Y271.prise} node[anchor=base west, yshift=-0.2em] {4\%};
\end{axis}
\end{tikzpicture}

@@

	\bigskip
	\structure{Top view of the final pattern}\\
	\begin{tikzpicture}[inner sep=0, very thick]
	\setlength{\mylength}{\columnwidth}
	\node[anchor=north west] (a) {\includegraphics[width=0.28\mylength]{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom2_crop}};
		\node[anchor=north] at (0.44\mylength,0) (b) {\includegraphics[width=0.28\mylength]{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom6_crop}};
		\node[anchor=north east] at (\mylength,0) (c) {\includegraphics[width=0.4\mylength]{cas3p2_fluo0p8_GDL4_50um_coating_2_transmission}};
		%zooms
		\node[minimum width = 0.137\mylength, minimum height=0.137\mylength, anchor=north west, draw=Accent2] at ($(a.north west) +(0.111\mylength,-0.072\mylength)$) (bz){};
		\draw[Accent2] (bz.north east) -- (b.north west) (bz.south east) -- (b.south west);
		\node[minimum width = 0.128\mylength, minimum height=0.081\mylength, anchor=north west, draw=Main] at ($(b.north west) +(0.097\mylength,-0.143\mylength)$) (cz){};
		\draw[Main] (cz.north east) -- (c.north west) (cz.south east) -- (c.south west);
		\node[minimum width = 0.156\mylength, minimum height=0.156\mylength, anchor=north west, draw=Accent1] at ($(c.north west) + (0.125\mylength,0)$) (dz) {};
		%scale bars
		\draw[ultra thick] (a.south east) ++(0,-0.25em) -- ++(-0.178\mylength,0) node[pos=0.5, below=0.25em, font=\small] (M) {\SI{1}{\centi\metre}};
		\draw[ultra thick] (b.south east) ++(0,-0.25em) -- ++(-0.176\mylength,0) node[pos=0.5, below=0.25em, font=\small] {\SI{5}{\milli\metre}};
		\draw[ultra thick] (c.south east) ++(0,-0.25em) -- ++(-0.132\mylength,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
	\end{tikzpicture}
\end{frame}

\begin{frame}{Dynamics (transmission macroscope)}
\movie[externalviewer]{\begin{tikzpicture}
\node[inner sep=0] (a) {\includegraphics[width=\textwidth]{prise_0799_resized.jpg}};
\draw[line width=0.2em] ++(a.north west) -- ++(0.177\textwidth,0) node[pos=0, above right, inner xsep=0] {\SI{1}{\milli\metre}};
\end{tikzpicture}
}{cas4_GDL_4_100um_coat_macroscope_2.avi}
\end{frame}

\begin{frame}{Dynamics (transmission macroscope)}
\begin{tikzpicture}
	\matrix[matrix of nodes, inner sep=0, column sep=0.015\textwidth, row sep=0.5em, ampersand replacement=\&] (m){
	33 min \& 38 min \& 43 min \\
	\includegraphics[width=0.32\textwidth]{prise_0100_color.jpg}\&
	\includegraphics[width=0.32\textwidth]{prise_0130_color.jpg}\&
	\includegraphics[width=0.32\textwidth]{prise_0160_color.jpg}\\
	48 min \& 1h \& 1h15 \\
	\includegraphics[width=0.32\textwidth]{prise_0190_color.jpg}\&
	\includegraphics[width=0.32\textwidth]{prise_0250_color.jpg}\&
	\includegraphics[width=0.32\textwidth]{prise_0360_color.jpg}\\
	};
	\draw[line width=0.2em] ++(m-4-1.south west) -- ++(0.056\textwidth,0) node[pos=0, below right, inner xsep=0] {\SI{1}{\milli\metre}};
\end{tikzpicture}

@@

\begin{tikzpicture}
\draw[ultra thick] (0,) -- +(0.786\textwidth,0) node[midway, above] {\SI{1}{\milli\metre}};
\end{tikzpicture}
\setlength{\tabcolsep}{1pt}
\begin{tabular}{p{\columnwidth}l}
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t000.png}& \SI{15}{\minute}\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t011.png} & \SI{22}{\minute}\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t110.png} & \SI{1}{\hour}~26\onslide<2->{\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t116.png} & \SI{1}{\hour}~30\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t117.png} & \SI{1}{\hour}~31\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t123.png} & \SI{1}{\hour}~35\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t200.png} & \SI{2}{\hour}~25\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t221.png} & \SI{2}{\hour}~40\\}
\end{tabular}

@@

\column{0.5\textwidth}
\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=g, group size=1 by 3,
			xticklabels at=edge bottom,
			vertical sep=0,
			},
		xmin=0, xmax=170, xtick={0,30,...,150},
		extra tick style={grid=major},%
		extra x ticks = {21,68}, extra x tick labels={},%
		scale only axis,
		width=\textwidth-4em,
		height=5\baselineskip,
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1em}
		]
	\nextgroupplot[
		ylabel={$G^\prime$ (\si{\pascal})},
		ymin=0,
		]
	\addplot+[no marks,Accent1] table[x expr={\thisrowno{0}/60}]{cas4_GDL4_Y271.prise};
	\node[below left] at (rel axis cs:1,1) {rheometer (stick)};

@@

\begin{frame}{Dynamics (confocal microscope)}
\movie[externalviewer]{\begin{tikzpicture}
	\node[inner sep=0] (a) {\includegraphics[width=\textwidth]{cas3p2_fluo0p8_GDL4_2_t260_crop_resized.jpg}};
	\draw[line width=0.2em] ++(a.south west) -- ++(0.75\textwidth,0) node[pos=0, below right, inner xsep=0] {\SI{1}{\milli\metre}};

@@

\begin{frame}{Dynamics (confocal microscope)}
\begin{tikzpicture}
	\matrix[matrix of nodes, inner sep=0, column sep=0.015\textwidth, row sep=0.5em, ampersand replacement=\&] (m){
	33 min \& 38 min \& 43 min \\
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t047_crop_resized.jpg}\&
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t056_crop_resized.jpg}\&
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t065_crop_resized.jpg}\\
	48 min \& 1h \& 1h15 \\
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t074_crop_resized.jpg}\&
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t092_crop_resized.jpg}\&
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t125_crop_resized.jpg}\\
	};
	\draw[line width=0.2em] ++(m-4-1.south west) -- ++(0.24\textwidth,0) node[pos=0, below right, inner xsep=0] {\SI{1}{\milli\metre}};
\end{tikzpicture}

@@

	\movie[externalviewer]{\includegraphics[width=\textwidth]{volume_cloque_t116}{volume_cloques_comp.avi}\\
	\begin{tikzpicture}
	\draw[ultra thick] (0,) -- +(0.786\textwidth,0) node[midway, below] {\SI{1}{\milli\metre}};
	\end{tikzpicture}

@@

\bigskip
\begin{itemize}
\item solvent must flow through gel
\begin{description}[$\ell_p$]
\item[$v$] gel velocity = -volumic flux $\simeq \SI{0.2}{\micro\metre\per\second}$
\item[$\ell_p$] pore size $ \approx \SI{4}{\micro\metre}$
\end{description}
\item $\sigma$ is a Darcy pressure
\[\sigma = \Delta P \sim \eta h v/\ell_p^2\]
\item poroelastic length
\[ \lambda^* \sim \left(\frac{B \ell_p^2}{\eta v h}\right)^\frac{1}{3} \simeq \SI{2}{\milli\metre}\]
\end{itemize}
}{
\begin{tikzpicture}
\begin{axis}[
	width=\textwidth,
	height=0.6\textwidth,
	xmin=0, xmax=1000, xtick={0,250, 500, 750}, xlabel={position (\si{\micro\metre})},
	ymin=0, ymax=50, ylabel={altitude (\si{\micro\metre})},
	cycle list name=earthy,
	no marks,
	]
	\draw[ultra thick, Accent2] (axis cs:580,0) -- (axis cs:580,50);
	\foreach \x in {2,3,..., 8}
		\addplot table[y index=\x]{alts_bottom_cloque.txt};
\end{axis}
\end{tikzpicture}
\begin{itemize}
\item $\lambda$ frozen at ceiling touch 
\item $A=H\equiv e-h$
\item $\lambda \sim \epsilon^{-3/7} H \sim e$
	%\[ \epsilon \sim \left(\frac{\lambda}{e}\frac{e}{H}\right)^{-7/3} \simeq 0.6\% \]
\end{itemize}
}

\column{0.5\textwidth}
\begin{block}{Ruck in a rug}
\tikzsetnextfilename{ruck}%
\begin{tikzpicture}[ultra thick]
\begin{axis}[
	name=a,
	width=\textwidth, height=3\baselineskip, scale only axis,
	domain=-180:180, no markers, ymin=0, ymax=3,xmin=-180,xmax=180,
	axis lines=none, xtick=\empty,
	axis background/.style={fill=white},
	]
	\addplot+[Accent1]{cos(x)+1};
	\addplot+[Accent1]{cos(x)+1.5};
	\draw[->, Accent2, ultra thick] (axis cs:90,1.25) -- (axis cs:90,2.25) node[pos=1, right] {$v$};
	\draw[Main, ultra thick, {Circle}->] (axis cs:-90,1.5) -- (axis cs:-90,0.25) node[right] {$\sigma$};
	%\node[above] at (axis cs:-90,1.5) {$P_2$};
	%\node[below right] at (axis cs:-90,1.25) {$P_1$};
	\draw[<->, ultra thick] (axis cs:0,0) -- (axis cs:0,2) node[midway, right] {$A$};
	\draw[<->] (axis cs:0,2) -- (axis cs:0,2.5) node[midway, right] {$h$};
\end{axis}
\fill[pattern=north east lines,pattern color=Accent2] (a.south west) rectangle ($(a.south east)+(0,-1em)$);
\draw[<->] ($(a.south west)+(0,-1.1em)$) -- ($(a.south east)+(0,-1.1em)$) node[midway, below] {$\lambda$};
\end{tikzpicture}

@@

\begin{frame}{No initial contact with a substrate}
\structure{Poiseuille vs Darcy on a flying carpet}
\begin{tikzpicture}
\begin{axis}[
	name=a,
	width=\textwidth, height=0.25\textwidth, scale only axis,
	domain=0:360, no markers, ymin=-4, ymax=4,xmin=0,xmax=360,
	axis lines=none, xtick=\empty,
	]
	\fill[gray!20] (axis cs:85,4) rectangle (axis cs:95,-4) (axis cs:265,4) rectangle (axis cs:275,-4);
	\addplot+[Accent1]{sin(x)+0.5};
	\addplot+[Accent1]{sin(x)-0.5};
	\addplot+[dashed, black]{0.5};
	\addplot+[dashed, black]{-0.5};
	\draw[<->, help lines] (axis cs:180,0.5) -- (axis cs:180,4) node[midway, left] {$H$}; 
	\draw[<->, help lines] (axis cs:30,-0.5) -- (axis cs:30,-4) node[midway, left] {$H$};
	\node[below] at (axis cs:90,-1.5) (pb1) {$P_1$};
	\node[above] at (axis cs:90,1.5) (ph2) {$P_2$};
	\node[above] at (axis cs:270,1.5) (ph1) {$P_1$};
	\node[below] at (axis cs:270,-1.5) (pb2) {$P_2$};
	\draw[line width=0.1em, ->] (ph2) -- (axis cs:90,0.5) node[midway, left] {Darcy} node[midway, right] {$v$};
	\draw[line width=0.1em, ->] (pb2) -- (pb1) node[midway, above] {Poiseuille} node[midway, below] {$u \sim \frac{\lambda}{H} v$};
\end{axis}
\fill[pattern=north east lines,pattern color=Accent2] (a.south west) rectangle +(\textwidth,-1em) (a.north west) rectangle +(\textwidth,1em);
\end{tikzpicture}

@@

%\tikzset{external/force remake}
\begin{frame}{Cell thickness}
\begin{tikzpicture}[mark size={0.3em}]
	\matrix[matrix of nodes, inner sep=0, column sep=0.01\columnwidth, row sep=0.01\columnwidth, ampersand replacement=\&] (m) {
		\includegraphics[width=0.245\columnwidth]{pattern_50um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_100um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_250um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_450um.jpg}\\
	};
	\node[inner sep=0, below left=0.01\columnwidth and 0 of m.south east] (x800) {\includegraphics[width=0.49\columnwidth]{pattern_800um_x1.jpg}};
	\draw[ultra thick, Accent2, <->] (x800.south west) ++(0.196\columnwidth, 0.05\columnwidth) -- ++(0.145\columnwidth,0) node[midway,above]{$\lambda$};
	\draw[line width=0.2em,Main](x800.north east) -- ++(-0.217\columnwidth,0) node[midway,below] {\SI{5}{\milli\metre}};

@@

\tikzset{external/force remake}
\begin{frame}{Surprising viscosity influence}
\begin{columns}
\column{0.5\textwidth}
\[ \lambda^* \sim \left(\frac{B \ell_p^2}{\eta v h}\right)^\frac{1}{3}\]
\begin{tikzpicture}
	\begin{loglogaxis}[%
		width=\textwidth,
		height=0.8\textwidth,
		xmin=0.6,xmax=11,xlabel={viscosity (\si{\milli\pascal\second})},
		xtick={0.7, 1, 2, 5, 10}, xticklabels={$0.7$, $1$, $2$, $5$, $10$},
		ytick={1,2,3,4}, yticklabels={$1$,$2$,$3$,$4$},
		ymin=1, ymax=5, ylabel={$\lambda$ (\si{\milli\metre})},
		mark size={0.3em},
		legend style={legend pos=south east},
		]
		\addplot+[no marks, domain=0.7:10, black, forget plot] {1.7*x^0.4} node[midway, below] {$\eta^{0.4}$};
		\addplot+[only marks,Accent1, mark=o] table{eta_lambda_eau_pure.txt};
		\addplot+[only marks,Accent2, mark=square] table{eta_lambda_eau_glycerol.txt};
		\legend{water, water-glycerol};
	\end{loglogaxis}
\end{tikzpicture}

>>>>

\bigskip
\begin{tabu}{X[c]X[c]c}
\includegraphics[height=0.3\textheight,clip=true,trim=3cm 7cm  2cm 5cm]{Mathieu}&
\includegraphics[height=0.3\textheight]{Thomas}&
\includegraphics[height=0.3\textheight]{Seb}\\
Mathieu Nespoulous & Thomas Gibaud & Sebastien Manneville\\
Associate Professor & CNRS researcher & Professor\\
Aix-Marseille Universit\'{e} & E.N.S. Lyon & E.N.S. Lyon\\
\end{tabu}

@@

%\tikzset{external/force remake}
\begin{frame}{Over-acidification: Faster but weaker}
\tikzsetnextfilename{gelation_GDL}
\begin{tikzpicture}
\begin{axis}[
	height=0.8\textheight,
	width=\textwidth,
	xlabel={time (h)}, ylabel={$G^\prime$ (\si{\pascal})},
	cycle list name=earthy,
	no marks,
	xmin=0, xmax=20,ymin=0,
	]
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1_Y265.prise} node[anchor=base west] {1\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1.25_Y277.prise} node[anchor=base west] {1.25\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1.5_Y275.prise} node[anchor=base west] {1.5\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL2_Y268.prise} node[anchor=base west] {2\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL3_Y270.prise} node[anchor=base west] {3\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL4_Y271.prise} node[anchor=base west, yshift=-0.2em] {4\%};
\end{axis}
\end{tikzpicture}

@@

	\bigskip
	\structure{Top view of the final pattern}\\
	\tikzsetnextfilename{patterns_zooms}
	\begin{tikzpicture}[inner sep=0, very thick]
	\setlength{\mylength}{\columnwidth}
	\node[anchor=north west] (a) {\includegraphics[width=0.28\mylength]{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom2_crop}};
		\node[anchor=north] at (0.44\mylength,0) (b) {\includegraphics[width=0.28\mylength]{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom6_crop}};
		\node[anchor=north east] at (\mylength,0) (c) {\includegraphics[width=0.4\mylength]{cas3p2_fluo0p8_GDL4_50um_coating_2_transmission}};
		%zooms
		\node[minimum width = 0.137\mylength, minimum height=0.137\mylength, anchor=north west, draw=Accent2] at ($(a.north west) +(0.111\mylength,-0.072\mylength)$) (bz){};
		\draw[Accent2] (bz.north east) -- (b.north west) (bz.south east) -- (b.south west);
		\node[minimum width = 0.128\mylength, minimum height=0.081\mylength, anchor=north west, draw=Main] at ($(b.north west) +(0.097\mylength,-0.143\mylength)$) (cz){};
		\draw[Main] (cz.north east) -- (c.north west) (cz.south east) -- (c.south west);
		\node[minimum width = 0.156\mylength, minimum height=0.156\mylength, anchor=north west, draw=Accent1] at ($(c.north west) + (0.125\mylength,0)$) (dz) {};
		%scale bars
		\draw[ultra thick] (a.south east) ++(0,-0.25em) -- ++(-0.178\mylength,0) node[pos=0.5, below=0.25em, font=\small] (M) {\SI{1}{\centi\metre}};
		\draw[ultra thick] (b.south east) ++(0,-0.25em) -- ++(-0.176\mylength,0) node[pos=0.5, below=0.25em, font=\small] {\SI{5}{\milli\metre}};
		\draw[ultra thick] (c.south east) ++(0,-0.25em) -- ++(-0.132\mylength,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
	\end{tikzpicture}
\end{frame}

\begin{frame}{Dynamics (transmission macroscope)}
\movie[externalviewer]{\tikzsetnextfilename{dynamics_still}\begin{tikzpicture}
\node[inner sep=0] (a) {\includegraphics[width=\textwidth]{prise_0799_resized.jpg}};
\draw[line width=0.2em] ++(a.north west) -- ++(0.177\textwidth,0) node[pos=0, above right, inner xsep=0] {\SI{1}{\milli\metre}};
\end{tikzpicture}
}{cas4_GDL_4_100um_coat_macroscope_2.avi}
\end{frame}

\begin{frame}{Dynamics (transmission macroscope)}
\tikzsetnextfilename{snapshots_macroscope}
\begin{tikzpicture}
	\matrix[matrix of nodes, inner sep=0, column sep=0.015\textwidth, row sep=0.5em, ampersand replacement=\&] (m){
	33 min \& 38 min \& 43 min \\
	\includegraphics[width=0.32\textwidth]{prise_0100_color.jpg}\&
	\includegraphics[width=0.32\textwidth]{prise_0130_color.jpg}\&
	\includegraphics[width=0.32\textwidth]{prise_0160_color.jpg}\\
	48 min \& 1h \& 1h15 \\
	\includegraphics[width=0.32\textwidth]{prise_0190_color.jpg}\&
	\includegraphics[width=0.32\textwidth]{prise_0250_color.jpg}\&
	\includegraphics[width=0.32\textwidth]{prise_0360_color.jpg}\\
	};
	\draw[line width=0.2em] ++(m-4-1.south west) -- ++(0.056\textwidth,0) node[pos=0, below right, inner xsep=0] {\SI{1}{\milli\metre}};
\end{tikzpicture}

@@

\tikzsetnextfilename{scalebar_fluo}
\begin{tikzpicture}
\draw[ultra thick] (0,) -- +(0.786\textwidth,0) node[midway, above] {\SI{1}{\milli\metre}};
\end{tikzpicture}
\setlength{\tabcolsep}{1pt}
\begin{tabular}{p{\columnwidth}l}
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t000.png}& \SI{15}{\minute}\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t011.png} & \SI{22}{\minute}\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t110.png} & \SI{1}{\hour}~26\onslide<2->{\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t116.png} & \SI{1}{\hour}~30\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t117.png} & \SI{1}{\hour}~31\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t123.png} & \SI{1}{\hour}~35\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t200.png} & \SI{2}{\hour}~25\\
	\includegraphics[width=\columnwidth, height=0.061\columnwidth]{coupe_cloque_t221.png} & \SI{2}{\hour}~40\\}
\end{tabular}

@@

\column{0.5\textwidth}
\tikzsetnextfilename{volume_area}
\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=g, group size=1 by 3,
			xticklabels at=edge bottom,
			vertical sep=0,
			},
		xmin=0, xmax=170, xtick={0,30,...,150},
		extra tick style={grid=major},%
		extra x ticks = {21,68}, extra x tick labels={},%
		scale only axis,
		width=\textwidth-4em,
		height=5\baselineskip,
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1em}
		]
	\nextgroupplot[
		ylabel={$G^\prime$ (\si{\pascal})},
		ymin=0,
		]
	\addplot+[no marks,Accent1] table[x expr={\thisrowno{0}/60}]{cas4_GDL4_Y271.prise};
	\node[below left] at (rel axis cs:1,1) {rheometer (stick)};

@@

\begin{frame}{Dynamics (confocal microscope)}
\tikzsetnextfilename{dynamics_confocal_still}
\movie[externalviewer]{\begin{tikzpicture}
	\node[inner sep=0] (a) {\includegraphics[width=\textwidth]{cas3p2_fluo0p8_GDL4_2_t260_crop_resized.jpg}};
	\draw[line width=0.2em] ++(a.south west) -- ++(0.75\textwidth,0) node[pos=0, below right, inner xsep=0] {\SI{1}{\milli\metre}};

@@

\begin{frame}{Dynamics (confocal microscope)}
\tikzsetnextfilename{snapshots_confocal}
\begin{tikzpicture}
	\matrix[matrix of nodes, inner sep=0, column sep=0.015\textwidth, row sep=0.5em, ampersand replacement=\&] (m){
	33 min \& 38 min \& 43 min \\
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t047_crop_resized.jpg}\&
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t056_crop_resized.jpg}\&
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t065_crop_resized.jpg}\\
	48 min \& 1h \& 1h15 \\
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t074_crop_resized.jpg}\&
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t092_crop_resized.jpg}\&
	\includegraphics[width=0.32\textwidth]{cas3p2_fluo0p8_GDL4_2_t125_crop_resized.jpg}\\
	};
	\draw[line width=0.2em] ++(m-4-1.south west) -- ++(0.24\textwidth,0) node[pos=0, below right, inner xsep=0] {\SI{1}{\milli\metre}};
\end{tikzpicture}

@@

	\movie[externalviewer]{\includegraphics[width=\textwidth]{volume_cloque_t116}}{volume_cloques_comp.avi}\\
	\only<1>{\tikzsetnextfilename{cloques_still}
	\begin{tikzpicture}
	\draw[ultra thick] (0,) -- +(0.786\textwidth,0) node[midway, below] {\SI{1}{\milli\metre}};
	\end{tikzpicture}}

@@

\bigskip
\begin{itemize}
\item solvent must flow through gel
\begin{description}[$\ell_p$]
\item[$v$] gel velocity = -volumic flux $\simeq \SI{0.2}{\micro\metre\per\second}$
\item[$\ell_p$] pore size $ \approx \SI{4}{\micro\metre}$
\end{description}
\item $\sigma$ is a Darcy pressure
\[\sigma = \Delta P \sim \eta h v/\ell_p^2\]
\item poroelastic length
\[ \lambda^* \sim \left(\frac{B \ell_p^2}{\eta v h}\right)^\frac{1}{3} \simeq \SI{2}{\milli\metre}\]
\end{itemize}
}{
\tikzsetnextfilename{alts_bottom_cloque}
\begin{tikzpicture}
\begin{axis}[
	width=\textwidth,
	height=0.6\textwidth,
	xmin=0, xmax=1000, xtick={0,250, 500, 750}, xlabel={position (\si{\micro\metre})},
	ymin=0, ymax=50, ylabel={altitude (\si{\micro\metre})},
	cycle list name=earthy,
	no marks,
	]
	\draw[ultra thick, Accent2] (axis cs:580,0) -- (axis cs:580,50);
	\foreach \x in {2,3,..., 8}
		\addplot table[y index=\x]{alts_bottom_cloque.txt};
\end{axis}
\end{tikzpicture}
\begin{itemize}
\item $\lambda$ frozen at ceiling touch 
\item $A=H\equiv e-h$
\item $\lambda \sim \epsilon^{-3/7} H \sim e$
	%\[ \epsilon \sim \left(\frac{\lambda}{e}\frac{e}{H}\right)^{-7/3} \simeq 0.6\% \]
\end{itemize}
}

\column{0.5\textwidth}
\begin{block}{Ruck in a rug}
\tikzsetnextfilename{ruck}%
\begin{tikzpicture}[ultra thick]
\begin{axis}[
	name=a,
	width=\textwidth, height=3\baselineskip, scale only axis,
	domain=-180:180, no markers, ymin=0, ymax=3,xmin=-180,xmax=180,
	axis lines=none, xtick=\empty,
	axis background/.style={fill=white},
	]
	\addplot+[Accent1]{cos(x)+1};
	\addplot+[Accent1]{cos(x)+1.5};
	\draw[->, Accent2, ultra thick] (axis cs:90,1.25) -- (axis cs:90,2.25) node[pos=1, right] {$v$};
	\draw[Main, ultra thick,->] (axis cs:-90,1.5) -- (axis cs:-90,0.25) node[right] {$\sigma$};
	%\node[above] at (axis cs:-90,1.5) {$P_2$};
	%\node[below right] at (axis cs:-90,1.25) {$P_1$};
	\draw[<->, ultra thick] (axis cs:0,0) -- (axis cs:0,2) node[midway, right] {$A$};
	\draw[<->] (axis cs:0,2) -- (axis cs:0,2.5) node[midway, right] {$h$};
\end{axis}
\fill[pattern=north east lines,pattern color=Accent2] (a.south west) rectangle ($(a.south east)+(0,-1em)$);
\draw[<->] ($(a.south west)+(0,-1.1em)$) -- ($(a.south east)+(0,-1.1em)$) node[midway, below] {$\lambda$};
\end{tikzpicture}

@@

\begin{frame}{No initial contact with a substrate}
\structure{Poiseuille vs Darcy on a flying carpet}
\tikzsetnextfilename{flying_carpet}%
\begin{tikzpicture}
\begin{axis}[
	name=a,
	width=\textwidth, height=0.25\textwidth, scale only axis,
	domain=0:360, no markers, ymin=-4, ymax=4,xmin=0,xmax=360,
	axis lines=none, xtick=\empty,
	]
	\fill[gray!20] (axis cs:85,4) rectangle (axis cs:95,-4) (axis cs:265,4) rectangle (axis cs:275,-4);
	\addplot+[Accent1]{sin(x)+0.5};
	\addplot+[Accent1]{sin(x)-0.5};
	\addplot+[dashed, black]{0.5};
	\addplot+[dashed, black]{-0.5};
	\draw[<->, help lines] (axis cs:180,0.5) -- (axis cs:180,4) node[midway, left] {$H$}; 
	\draw[<->, help lines] (axis cs:30,-0.5) -- (axis cs:30,-4) node[midway, left] {$H$};
	\node[below] at (axis cs:90,-1.5) (pb1) {$P_1$};
	\node[above] at (axis cs:90,1.5) (ph2) {$P_2$};
	\node[above] at (axis cs:270,1.5) (ph1) {$P_1$};
	\node[below] at (axis cs:270,-1.5) (pb2) {$P_2$};
	\draw[line width=0.1em, ->] (ph2) -- (axis cs:90,0.5) node[midway, left] {Darcy} node[midway, right] {$v$};
	\draw[line width=0.1em, ->] (pb2) -- (pb1) node[midway, above] {Poiseuille} node[midway, below] {$u \sim \frac{\lambda}{H} v$};
\end{axis}
\fill[pattern=north east lines,pattern color=Accent2] (a.south west) rectangle +(\textwidth,-1em) (a.north west) rectangle +(\textwidth,1em);
\end{tikzpicture}

@@

%\tikzset{external/force remake}
\begin{frame}{Cell thickness}
\tikzsetnextfilename{thickness}
\begin{tikzpicture}[mark size={0.3em}]
	\matrix[matrix of nodes, inner sep=0, column sep=0.01\columnwidth, row sep=0.01\columnwidth, ampersand replacement=\&] (m) {
		\includegraphics[width=0.245\columnwidth]{pattern_50um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_100um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_250um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_450um.jpg}\\
	};
	\node[inner sep=0, below left=0.01\columnwidth and 0 of m.south east] (x800) {\includegraphics[width=0.49\columnwidth]{pattern_800um_x1.jpg}};
	\draw[ultra thick, Accent2, <->] (x800.south west) ++(0.196\columnwidth, 0.05\columnwidth) -- ++(0.145\columnwidth,0) node[midway,above]{$\lambda$};
	\draw[line width=0.2em,Main](x800.north east) -- ++(-0.217\columnwidth,0) node[midway,below] {\SI{5}{\milli\metre}};

@@

%\tikzset{external/force remake}
\begin{frame}{Surprising viscosity influence}
\begin{columns}
\column{0.5\textwidth}
\[ \lambda^* \sim \left(\frac{B \ell_p^2}{\eta v h}\right)^\frac{1}{3}\]
\tikzsetnextfilename{viscosity_dependence}
\begin{tikzpicture}
	\begin{loglogaxis}[%
		width=\textwidth,
		height=0.8\textwidth,
		xmin=0.6,xmax=11,xlabel={viscosity (\si{\milli\pascal\second})},
		xtick={0.7, 1, 2, 5, 10}, xticklabels={$0.7$, $1$, $2$, $5$, $10$},
		ytick={1,2,3,4}, yticklabels={$1$,$2$,$3$,$4$},
		ymin=1, ymax=5, ylabel={$\lambda$ (\si{\milli\metre})},
		mark size={0.3em},
		legend style={legend pos=south east},
		]
		\addplot+[no marks, domain=0.7:10, black, forget plot] {1.7*x^0.4} node[midway, below] {$\eta^{0.4}$};
		\addplot+[only marks,Accent1, mark=o] table{eta_lambda_eau_pure.txt};
		\addplot+[only marks,Accent2, mark=square] table{eta_lambda_eau_glycerol.txt};
		\legend{water, water-glycerol};
	\end{loglogaxis}
\end{tikzpicture}
